Target Markdown

### 2023-08-07 _targets.Rmd
test

```{targets raw_sim}
list(
  tar_target(var_param_sim, c("rep", "productivity", "S", "ct", "rho", "env_stoch", "Z")),
  tar_target(sim_files_out, list.files(here::here("res", "simCSZenrich3/simCSZenrich3"))),
  tar_target(sim_files_ts,
    list.files(here::here("res", "simCSZenrich3")) %>% #
      .[str_detect(., "_ts")]
    ),
  tar_target(sim_param,
    map_dfr(sim_files_out,
      function (x) {
        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", x),
          format = "arrow") %>%
        collect() %>%
        select(all_of(var_param_sim))
      })
    ),
  # Because I had to remove one ts that failed...
  tar_target(sim_param_ts,
    map_dfr(str_remove(sim_files_ts, "_ts")[str_remove(sim_files_ts, "_ts") %in% sim_files_out],
      function (x) {
        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", x),
          format = "arrow") %>%
        collect() %>%
        select(all_of(var_param_sim))
      })
  ),
  tar_target(sim_prep,
        open_dataset(here::here("res", "simCSZenrich3/simCSZenrich3", sim_files_out),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!is.na(richness)) %>%
        mutate(across(c(int_strength, max_int),
            ~map2(.x, S,
              function(y, rich) {
                matrix(y, nrow = rich)
              }
          ) %>%
        # Get matrix of alive species
        mutate(max_int_alive  = map2(max_int, bm_sp,
            function(mat, bm) {
              mask <- bm > 10^-6
              mat[mask, mask, drop = FALSE]
            }
        ) %>%
        select(-max_int),
        pattern = sim_files_out
      ),
  tar_target(sim_net,
    sim_prep %>%
      mutate(
        persistence = richness / S,
        async = 1 / sync,
        stab_pop = 1 / avg_cv_sp,
        ct_alive = map_dbl(max_int_alive,
          ~ifelse(sum(.x) == 0, 0,
            sum(.x > 0) / ((ncol(.x))^2))),
        max_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
          ),
        avg_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
          ),
        sd_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
          ),
        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
        inv_sd_max_int_alive = 1 / sd_max_int_alive,
        gini_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0]))),
        avg_omnivory = map_dbl(omnivory, mean),
        disconnected_prod = map_lgl(max_int_alive,
          ~any(colSums(.x) == 0 & rowSums(.x) == 0))
        ) %>%
    select(!where(is.list))
  ),
  tar_target(sim_ts2_null,
    open_dataset(here::here("res", "simCSZenrich3", sim_files_ts),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        mutate(is_null = map_lgl(species, is.null)) %>%
        select(is_null),
        pattern = sim_files_ts
        ),
  tar_target(sim_ts2,
    open_dataset(here::here("res", "simCSZenrich3", sim_files_ts),
          format = "arrow") %>%
        collect() %>%
        # Transform back interaction strength into matrices
        mutate(across(where(is.list), as.list)) %>%
        filter(!map_lgl(species, is.null)) %>%
        mutate(
          stoch_d = map2(species, stoch, function(bm, d_stoch) {
            .1 * bm * exp(d_stoch)
            }),
          species = map(species, ~matrix(.x, nrow = 100)),
          stoch = map(stoch, ~matrix(.x, nrow = 100)),
          stoch_d = map(stoch_d, ~matrix(.x, nrow = 100)),
          cpe = map_dbl(species, compensatory_effect),
          cpe_env = map_dbl(stoch_d, compensatory_effect),
          cpe_int = cpe / cpe_env,
          stab_com = map_dbl(species, community_stability),
          pop_stab = map_dbl(species, population_stability),
          bm_sp = map(species, ~colMeans(.x)),
          bm_total = map_dbl(bm_sp, ~sum(.x)),
          sd_sp = map(species, ~apply(.x, 2, sd)),
          sum_sd_sp = map_dbl(sd_sp, ~sum(.x)),
          async = map_dbl(species, asynchrony),
          sae = map(species, statistical_averaging_effect),
          sae_total = map_dbl(sae, ~.x["total"]),
          sae_even = map_dbl(sae, ~.x["even"]),
          evenness_sae = map_dbl(sae, ~.x["eveness"])
        ) %>%
        select(-species, -stoch_d, -stoch),
        pattern = sim_files_ts
  ),
  tar_target(sim_stab, cbind(sim_param[!sim_ts2_null$is_null,], sim_ts2) %>% as_tibble()),
  tar_target(sim, left_join(sim_net %>% select(-async, -stab_com), sim_stab, by = var_param_sim)),
  tar_target(sim_fw,
    sim %>%
      filter(
        max_tlvl > 1,
        sum_sd_sp != Inf,
        bm_total > 10^-5,
        !disconnected_prod
   ),
   tar_target(sim_fw_df, as.data.frame(sim_fw))

@@

## Species bm, sd and tlvl

```{targets sim_sp, tar_simple = TRUE}
sim_stab %>%
  select(all_of(c(var_param_sim, "sd_sp", "bm_sp"))) %>%
  left_join(
    sim_prep %>%
      select(all_of(c(var_param_sim, "tlvl", "alive_species")))
  ) %>%
  mutate(
    sd_sp = map2(sd_sp, alive_species, ~.x[.y]),
    bm_sp = map2(bm_sp, alive_species, ~.x[.y]),
    cv_sp = map2(sd_sp, bm_sp, ~.x / .y),
    tlvl_bm_sd_sp = pmap(list(tlvl, bm_sp, sd_sp, cv_sp, alive_species),
      function(x, y, z, a, b) {
        rbind.data.frame(list(
        species = b,
            tlvl = x,
            bm_sp = y,
            sd_sp = z,
            cv_sp = a
        )
        )
      }),
    check = map_lgl(tlvl_bm_sd_sp, ~is.null(nrow(.x)))
  ) %>%
  filter(!check) %>%
  select(all_of(c(var_param_sim, "tlvl_bm_sd_sp"))) %>%
  unnest(c(tlvl_bm_sd_sp))
```

>>>>

```{r targets raw_sim}
list(
)

@@
